\documentclass[oneside, letterpaper, 10pt, oldfontcommands]{memoir}
\input{thesis-preamble}
%\bibliographystyle{ieeetr}
\addbibresource{results/HESE_Final_Paper/hesebiblio.bib}
\addbibresource{results/mcllh_paper/likelihood.bib}
\addbibresource{results/passing_fractions_paper/nuveto.bib}
\addbibresource{thesis-citations.bib}
\setlrmarginsandblock{1in}{1in}{*}
\setulmarginsandblock{1in}{1in}{*}
\checkandfixthelayout
\setsecnumdepth{paragraph}
\maxtocdepth{subsection}

\linenumbers{}

\begin{document}


\frontmatter

\thetitlepage
\cleardoublepage
\setcounter{page}{1}

%\section{Abstract}
%\uwabstract
%\cleardoublepage

\section{Acknowledgements}

The body of work that follows tells a story of scientific achievement, highlighting the incremental progress others and I have made. However, it neglects something far more important, the people and community behind it all. Unfortunately, I have neither the time nor space to thank everyone properly. I have had incredible support from friends, family, mentors, communities of fellow scientists, among many others throughout this journey. Without their help, support, and constant positive influence, I would not be where I am now, nor would I be the person I am today.

Thank you, Albrecht, for your guidance, light-hearted perspective, and prudent advice. Your persistent input has helped me become a better scientist and communicator, despite my own stubbornness at times. There is still much for me to learn, but I have you to thank for setting me on the right track and keeping me from getting lost in the metaphorical woods. Carlos, Tianlu, Juliana, and Nancy, we've shared a long and challenging road bringing our analyses to fruition. Still, I hope you all remember some of the fun we had along the way. You all pushed me to be better in different ways, and it has been a blast having you as collaborators. I'm fortunate to have been surrounded by the fantastic people at WIPAC. I couldn't ask for a better bunch as friends and colleagues to accompany me through these years. Your attitudes, eagerness, and excitement have been absolutely contagious, and I have been humbled by your generosity and selfless drive to improve the institutions that shape our lives. I hope to see you all in the future, even as we depart from our shared experiences at WIPAC.

To my parents, Margaret and James, thank you for your unconditional love and support. You've been there for me at every turn.

\clearpage
\tableofcontents\clearpage
%\listoffigures\clearpage
%\listoftables\clearpage

\mainmatter
%\linenumbers

\include{chapters/introduction}
\include{chapters/background}
\include{chapters/icecube}
\include{chapters/selection}
\include{chapters/reconstruction}
\include{chapters/backgrounds}
\include{chapters/statistics}
\include{chapters/results}
\include{chapters/conclusions}


%\bibliography{results/HESE_Final_Paper/hesebiblio,results/mcllh_paper/likelihood,results/passing_fractions_paper/nuveto,thesis-citations}


\chapter*[Bibliography]{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography[heading=none]
\refstepcounter{chapter}

\clearpage
\newpage
\appendix

\begingroup
\graphicspath{{results/HESE_Final_Paper/}}
\chapter{HESE source searches}
\section{High-energy astrophysical neutrino source searches\label{sec:sources}}
\subfile{results/HESE_Final_Paper/sections/sources}
\section{Event comparison\label{sec:comparison}}
\subfile{results/HESE_Final_Paper/appendices/comparison}
\section{Source catalog\label{sec:source_catalog}}
\subfile{results/HESE_Final_Paper/appendices/sources_table}

\chapter{HESE diffuse flux measurements}
%\section{Expected number of events table\label{sec:events_table}}
%\subfile{results/HESE_Final_Paper/appendices/event_table}
%\section{Sideband distributions\label{sec:sidebands}}
%\subfile{results/HESE_Final_Paper/appendices/sidebands}
%\section{Effects of systematics in analysis distributions\label{sec:extendedsys}}
%\subfile{results/HESE_Final_Paper/appendices/extendedsys}
\section{Data release for additional characterization of the astrophysical neutrino flux\label{sec:release}}
\subfile{results/HESE_Final_Paper/appendices/release}
\endgroup

\end{document}
